Plots

### 2025-05-23 manuscript/manuscript.tex
Added data profile by age range

\section{Data Exploration}\label{app-data}

@@

>>>>

\section{Data Profile}\label{app-data}

@@

\begin{sidewaystable}
\caption{Case study data by cause of death.}\label{tab-data-cod}
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lllll}
    \toprule%
    Age Group  &  Cause of Death (COD)  &  Female  &  Male  &  Total  \\
    \midrule
    \makecell[l]{\\Adult (n=3826, 55.1\%, 18 CODs)\\Adult Female (n=1681, 43.9\%)\\Adult Male (n=2145, 56.1\%)}  &  Acute Respiratory Infections  &  48 (45.7\%)  &  57 (54.3\%)  &  105 (2.7\%)  \\ 
        &  Cancers  &  32 (65.3\%)  &  17 (34.7\%)  &  49 (1.3\%)  \\ 
        &  Chronic Respiratory Diseases  &  29 (38.7\%)  &  46 (61.3\%)  &  75 (2\%)  \\ 
        &  Diabetes Mellitus  &  14 (51.9\%)  &  13 (48.1\%)  &  27 (0.7\%)  \\ 
        &  Diarrhoeal Diseases  &  102 (49.8\%)  &  103 (50.2\%)  &  205 (5.4\%)  \\ 
        &  Ill-Defined  &  56 (47.9\%)  &  61 (52.1\%)  &  117 (3.1\%)  \\ 
        &  Ischemic Heart Disease  &  89 (53\%)  &  79 (47\%)  &  168 (4.4\%)  \\ 
        &  Liver And Alcohol Related Diseases  &  58 (45.3\%)  &  70 (54.7\%)  &  128 (3.3\%)  \\ 
        &  Malaria  &  372 (46.6\%)  &  427 (53.4\%)  &  799 (20.9\%)  \\ 
        &  Maternal Conditions  &  130 (100\%)  &  N/A  &  130 (3.4\%)  \\ 
        &  Other Cardiovascular Diseases  &  59 (55.1\%)  &  48 (44.9\%)  &  107 (2.8\%)  \\ 
        &  Other Noncommunicable Diseases  &  160 (38.6\%)  &  254 (61.4\%)  &  414 (10.8\%)  \\ 
        &  Other Injuries  &  83 (23.2\%)  &  274 (76.8\%)  &  357 (9.3\%)  \\ 
        &  Road And Transport Injuries  &  73 (29.1\%)  &  178 (70.9\%)  &  251 (6.6\%)  \\ 
        &  Stroke  &  147 (44.4\%)  &  184 (55.6\%)  &  331 (8.7\%)  \\ 
        &  Suicide  &  N/A  &  3 (100\%)  &  3 (0.1\%)  \\ 
        &  Tuberculosis  &  54 (31.6\%)  &  117 (68.4\%)  &  171 (4.5\%)  \\ 
        &  Unspecified Infections  &  175 (45\%)  &  214 (55\%)  &  389 (10.2\%)  \\ 
    \makecell[l]{\\Child (n=2636, 38\%, 9 CODs)\\Child Female (n=1290, 48.9\%)\\Child Male (n=1346, 51.1\%)}  &  Congenital Anomalies  &  1 (100\%)  &  N/A  &  1 (0\%)  \\ 
        &  Diarrhoeal Diseases  &  79 (45.1\%)  &  96 (54.9\%)  &  175 (6.6\%)  \\ 
        &  \makecell[l]{Epilepsy, Leukaemia, And\\Other Noncommunicable Diseases}  &  61 (53.5\%)  &  53 (46.5\%)  &  114 (4.3\%)  \\ 
        &  Ill-Defined  &  34 (48.6\%)  &  36 (51.4\%)  &  70 (2.7\%)  \\ 
        &  Injuries  &  51 (37.8\%)  &  84 (62.2\%)  &  135 (5.1\%)  \\ 
        &  Malaria  &  680 (49.2\%)  &  702 (50.8\%)  &  1382 (52.4\%)  \\ 
        &  Nutritional Deficiencies  &  7 (63.6\%)  &  4 (36.4\%)  &  11 (0.4\%)  \\ 
        &  Other Infections  &  338 (50.7\%)  &  329 (49.3\%)  &  667 (25.3\%)  \\ 
        &  Pneumonia  &  39 (48.1\%)  &  42 (51.9\%)  &  81 (3.1\%)  \\ 
    \makecell[l]{\\Neonate (n=477, 6.9\%, 7 CODs)\\Neonate Female (n=227, 47.6\%)\\Neonate Male (n=250, 52.4\%)}  &  Birth Asphyxia And Birth Trauma  &  38 (36.9\%)  &  65 (63.1\%)  &  103 (21.6\%)  \\ 
        &  Congenital Anomalies  &  2 (100\%)  &  N/A  &  2 (0.4\%)  \\ 
        &  Ill-Defined  &  11 (47.8\%)  &  12 (52.2\%)  &  23 (4.8\%)  \\ 
        &  Neonatal Infections  &  49 (49.5\%)  &  50 (50.5\%)  &  99 (20.8\%)  \\ 
        &  Other  &  2 (40\%)  &  3 (60\%)  &  5 (1\%)  \\ 
        &  Prematurity And Low Birthweight  &  39 (53.4\%)  &  34 (46.6\%)  &  73 (15.3\%)  \\ 
        &  Stillbirth  &  86 (50\%)  &  86 (50\%)  &  172 (36.1\%)  \\
    \botrule
\end{tabular*}
\end{sidewaystable}

\begin{table}
\caption{Case study data by age range.}\label{tab-data-age}
\begin{tabular}{@{}lllll@{}}
\toprule%
    Age Group  &  Age Range  &  Female  &  Male  &  Total  \\
    \midrule
        \makecell[l]{\\Adult (n=3826, 55.1\%, 18 CODs)\\Adult Female (n=1681, 43.9\%)\\Adult Male (n=2145, 56.1\%)}  &  10-14 Years  &  51 (37.8\%)  &  84 (62.2\%)  &  135 (3.5\%)  \\ 
        &  15-19 Years  &  115 (42.8\%)  &  154 (57.2\%)  &  269 (7\%)  \\ 
        &  20-24 Years  &  146 (53.1\%)  &  129 (46.9\%)  &  275 (7.2\%)  \\ 
        &  25-29 Years  &  159 (45.2\%)  &  193 (54.8\%)  &  352 (9.2\%)  \\ 
        &  30-34 Years  &  174 (50.9\%)  &  168 (49.1\%)  &  342 (8.9\%)  \\ 
        &  35-39 Years  &  153 (45.4\%)  &  184 (54.6\%)  &  337 (8.8\%)  \\ 
        &  40-44 Years  &  134 (42\%)  &  185 (58\%)  &  319 (8.3\%)  \\ 
        &  45-49 Years  &  148 (47\%)  &  167 (53\%)  &  315 (8.2\%)  \\ 
        &  50-54 Years  &  134 (39.6\%)  &  204 (60.4\%)  &  338 (8.8\%)  \\ 
        &  55-59 Years  &  96 (37.6\%)  &  159 (62.4\%)  &  255 (6.7\%)  \\ 
        &  60-64 Years  &  128 (40.8\%)  &  186 (59.2\%)  &  314 (8.2\%)  \\ 
        &  65-69 Years  &  243 (42.3\%)  &  332 (57.7\%)  &  575 (15\%)  \\ 
        \makecell[l]{\\Child (n=2636, 38\%, 9 CODs)\\Child Female (n=1290, 48.9\%)\\Child Male (n=1346, 51.1\%)}  &  1-5 Months  &  146 (47.4\%)  &  162 (52.6\%)  &  308 (11.7\%)  \\ 
        &  6-11 Months  &  160 (50.8\%)  &  155 (49.2\%)  &  315 (11.9\%)  \\ 
        &  1-5 Years  &  822 (50.3\%)  &  811 (49.7\%)  &  1633 (61.9\%)  \\ 
        &  6-11 Years  &  162 (42.6\%)  &  218 (57.4\%)  &  380 (14.4\%)  \\ 
        \makecell[l]{\\Neonate (n=477, 6.9\%, 7 CODs)\\Neonate Female (n=227, 47.6\%)\\Neonate Male (n=250, 52.4\%)}  &  0-6 Days  &  184 (46.6\%)  &  211 (53.4\%)  &  395 (82.8\%)  \\ 
        &  7-27 Days  &  43 (52.4\%)  &  39 (47.6\%)  &  82 (17.2\%)  \\
    \botrule
\end{tabular}
\end{table}

### 2025-05-23 src/plots.Rmd
Added data profile by age range

# Build the table
tab_cod_html <- tab_cod_format %>%
    kable(format = "html", escape = FALSE, align = "l") %>%
    kable_styling(full_width = FALSE, position = "left", html_font = "Arial") %>%
    row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
    row_spec(nrow(df_selected), extra_css = "border-bottom: 2px solid;")
tab_cod_html
```

@@

# Get n records by age
tab_age_n <- df %>%
    group_by(age, physician_cghr10) %>%
    summarize(n_cod = n())

@@

>>>>

# Build the table
tab_cod_html <- tab_cod_format %>%
    kable(format = "html", escape = FALSE, align = "l") %>%
    kable_styling(full_width = FALSE, position = "left", html_font = "Arial") %>%
    row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
    row_spec(nrow(tab_cod_format), extra_css = "border-bottom: 2px solid;")
tab_cod_html

@@

# Get n records by age
tab_age_n <- df %>%
    group_by(age, age_range) %>%
    summarize(n_age = n())

# Get n records by age and sex
tab_age_sex <- df %>%
    group_by(age, age_range, sex) %>%
    summarize(n_age_sex = n()) %>%
    pivot_wider(
        names_from = sex,
        values_from = n_age_sex,
        names_glue = "n_age_{str_to_lower(sex)}"
    )

# Combine all
tab_age <- tab_age_n %>%
    left_join(tab_agegroup, by = "age") %>%
    left_join(tab_agegroup_sex, by = "age") %>%
    left_join(tab_age_sex, by = c("age", "age_range"))

# Calc perc
tab_age <- tab_age %>%
    mutate(
        n_perc = round(n / nrow(df) * 100, 1),
        n_male_perc = round(n_male / n * 100, 1),
        n_female_perc = round(n_female / n * 100, 1),
        n_age_perc = round(n_age / n * 100, 1),
        n_age_male_perc = round(n_age_male / n_age * 100, 1),
        n_age_female_perc = round(n_age_female / n_age * 100, 1)
    ) %>%
    ungroup

# Add labels to combined
tab_age <- tab_age %>%
    mutate(
        age = if_else(age == "neo", "Neonate", str_to_title(age)),
        `Age Group` = glue(
            "{age} (n={n}, {n_perc}%, {n_cod_uniq} CODs)\n{age} Female (n={n_female}, {n_female_perc}%)\n{age} Male (n={n_male}, {n_male_perc}%)"
        ),
        `Age Range` = glue(
            "{str_to_title(age_range)}"
        ),
        `Female` = glue("{n_age_female} ({n_age_female_perc}%)"),
        `Male` = glue("{n_age_male} ({n_age_male_perc}%)"),
        `Total` = glue("{n_age} ({n_age_perc}%)")
    ) %>%
    mutate(across(
        c(`Female`, `Male`, `Total`),
        ~ if_else(.x == "NA (NA%)", NA, .x)
    ))

# Save table
write_csv(tab_age, "../data/healsl_rd1to2_age_profile_v1.csv", na = "")

# Display table
tab_age

@@

# Prepare and format the data
tab_age_format <- tab_age %>%
    ungroup %>%
    select(`Age Group`, `Age Range`, Female, Male, Total) %>%
    mutate(
        `Age Group` = str_replace_all(`Age Group`, "\\\\n|\\n", "<br>"),
        `Age Range` = str_replace_all(`Age Range`, "\\\\n|\\n", "<br>")
    ) %>%
    group_by(`Age Group`) %>%
    mutate(`Age Group` = ifelse(row_number() == 1, `Age Group`, "")) %>%
    ungroup()

# Build the table
tab_age_html <- tab_age_format %>%
    kable(format = "html", escape = FALSE, align = "l") %>%
    kable_styling(full_width = FALSE, position = "left", html_font = "Arial") %>%
    row_spec(0, extra_css = "border-top: 2px solid; border-bottom: 1px solid;") %>%     # thick top border
    row_spec(nrow(tab_age_format), extra_css = "border-bottom: 2px solid;")
tab_age_html
